Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-10-05 manuscript.Rmd

print(table1)

@@

```{r Figure 1 Small Multiples Paper}
#scopus.df < scopus.df %>% filter(Year <= 2013)

@@

# Create Scopus labels for the facets

scopus.df$Year <- as.numeric(scopus.df$Year)
scopus.df <- filter(scopus.df, Year <= 2013)
scopus.df$Year <- as.numeric(scopus.df$Year)
scopus_annotate <- filter(scopus.df, Year <= 2013) %>%
  group_by(Journal) %>%
  summarize(N = pretty(sum(Documents)))

@@

 abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 80)
 ypos = rep(200, 80)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
     rename(Abbrev = Overall.N.Abbrev)

@@

 library(grid)
 library(gridExtra)
# Plotting function    
# 
 plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 8)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")

print(plotSmallMultiples.1)
print(plotSmallMultiples.2)
```

@@

exp.0321 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.0321[i] <- exp.0321[i-1] + exp.0321[i-1]*.0321
}

n.journals.year$Price <- exp.047
n.journals.year$SWHD <- exp.0321
n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
n.journals.year <- as.data.frame(n.journals.year)

@@

cols = c("Observed Growth" = cp[1], "3.21% CAGR" = cp[4], "4.7% CAGR" = cp[3])

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

#ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)

@@

>>>>

print(table1)
```

@@

```{r Figure 1 Small Multiples Paper}

@@

# Create Scopus labels for the facets
scopus.df$Year <- as.numeric(scopus.df$Year)
scopus.df <- filter(scopus.df, Year <= 2013)
scopus.df$Year <- as.numeric(scopus.df$Year)
scopus_annotate <- filter(scopus.df, Year <= 2013) %>%
  group_by(Journal) %>%
  summarize(N = pretty(sum(Documents)))

@@

abb.df$ID <- 1:nrow(abb.df)

sm.scopus.merged <- full_join(sm.scopus.merged, abb.df, by = "Journal") %>% 
  select(-X) %>%
  mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
  mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
  ungroup()

 # Create labels for the facets
Overall.N <- distinct(sm.scopus.merged, Abbrev) 
lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
lab <- paste(lab1, lab2, sep="\n")
xpos = rep(1999, 80)
ypos = rep(190, 80)
ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
  rename(Abbrev = Overall.N.Abbrev)

@@

# Plotting function    
# 
 plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  
   aes(Year, N)) +
  geom_line(colour="#e66101") +
  geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], 
    aes(Year, Documents), colour = "#533c99", alpha = .80) +  
  facet_wrap(~ Abbrev) + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8)) + 
  theme(legend.position = "bottom", 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
  geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
  ylim(c(0,225)) +
  scale_x_continuous(breaks=seq(1989, 2015, 8)) +
  annotate("segment", x = 1989, xend = 1992, y = 210, yend = 210, colour = "#e66101") + 
  annotate("segment", x = 1989, xend = 1992, y = 170, yend = 170, colour = "#533c99") +
  ggtitle("Number of Article Records by Journal, 1989 - 2013 (Part 1)")

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
  aes(Year, N)) +
  geom_line(colour="#e66101") +
  geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
  aes(Year, Documents), colour = "#533c99", alpha = .80) + 
  facet_wrap(~ Abbrev) + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8)) +  
  theme(legend.position = "bottom", 
  panel.grid.minor = element_blank(), 
  axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
  geom_text(data = ldata[41:80, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
  ylim(c(0,225)) +
  scale_x_continuous(breaks=seq(1989, 2015, 8)) +
  annotate("segment", x = 1989, xend = 1992, y = 210, yend = 210, colour = "#e66101") + 
  annotate("segment", x = 1989, xend = 1992, y = 170, yend = 170, colour = "#533c99") +
  ggtitle("Number of Article Records by Journal, 1989 - 2013 (Part 2)")

print(plotSmallMultiples.1)
print(plotSmallMultiples.2)

ggsave(plotSmallMultiples.1, file = "smallMultiples1.jpeg", width = 10, height = 7, units = "in", dpi=1200)

ggsave(plotSmallMultiples.2, file = "smallMultiples2.jpeg", width = 10, height = 7, units = "in", dpi=1200)
```

@@

exp.0307 <- c(29, rep(NA, 24)) 
for(i in 2:25){
    exp.0307[i] <- exp.0307[i-1] + exp.0307[i-1]*.0307
}

n.journals.year$Price <- exp.047
n.journals.year$SWHD <- exp.0307
n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
n.journals.year <- as.data.frame(n.journals.year)

@@

cols = c("Observed Growth" = cp[1], "3.07% CAGR" = cp[4], "4.7% CAGR" = cp[3])

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.07% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)

@@

```{r Linear Growth}

n.journals.year$yearCount <-  c(1:nrow(n.journals.year))
